---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Researcher burnout and QRP

<!-- badges: start -->

<!-- badges: end -->

## Folder structure

The `data/raw` folder contains all the datafiles that are needed to reproduce the results of the project.

The `analysis/` folder contains all the analyses files in quarto documents.

The `analysis/figures/` folder contains all the figures

## How to Reproduce the Analysis Using `{renv}`

1.  Install R and RStudio (optional):

-   [Download R](https://cran.r-project.org/bin/windows/base/)
-   [Download RStudio](https://posit.co/download/rstudio-desktop/) (if preferred)

2.  Install {renv} (if not already installed):

```{r, eval=FALSE}
install.packages("renv")
```

3.  Clone or Download This Project:

-   Clone via Git:

<!-- -->

```         
git clone https://github.com/DianovicsZsimi/emotional-landscape-researchers.git
```

-   Or download the ZIP file and extract it.

4.  Restore the Project Environment: Open the project in R (or RStudio) and run:

```{r, eval=FALSE}
renv::restore()
```

This command will:

-   Install the exact versions of all packages listed in `renv.lock`.
-   Ensure compatibility with the tested environment.
-   Installing the `renv` environment takes about 10 minutes on an average computer with Windows 11 64bit.

When trying to restore the environment on Mac, you may get the following error:

`ld: library 'gfortran' not found`

This is because the `gfortran` library is not installed or cannot be found.

To solve this, you may need to first install the gfortran library using Homebrew:

`brew install gcc`

(you can check this by running which gcc or gcc --version).

And then, tell R where to find `gfortran` by running the following code in the terminal at the project root:

```{r}
mkdir -p ~/.R
cat > ~/.R/Makevars << EOF
FC=$(which gfortran)
F77=$(which gfortran)
FLIBS=-L$(brew --prefix gcc)/lib/gcc/current
EOF
```


(If you are using Windows, `renv::restore()` will not work without RTools. You need RTools to compile some packages. You can install it by running: )

```{r, eval=FALSE}
install.packages("installr")
installr::install.Rtools()
```

5.  Run the analysis. Execute the scripts in this order:

I. raw_to_clean_data.qmd

II\. clean_to_processed_data.qmd

III\. descriptive_analysis.qmd
